Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-07 paper.tex
Feature unions + example

\texttt{FeatureUnion} objects

\vspace{3cm}

A distinguishing feature of \textit{scikit-learn} estimators
is that they can be composed into \texttt{Pipeline} objects.
Such objects combine typical machine learning workflows
(extracting features, centering/scaling/normalization,
feature selection, making predictions)
in a single object that is itself an estimator,
and whose methods cause data to flow through the pipeline.
More importantly, though, they can be used for
systematic, automated model selection.
This is best explained by example.

By composing, say, a \texttt{CountVectorizer} object
(which extracts term frequency features from text documents
according to a bag-words model),
a \textsf{tf--idf} transformer, a $\chi^2$ feature selector and a linear SVM,
one obtains a pipeline object with various hyperparameters:
whether to do stopword filtering,
linear vs.\ logarithmic \textsf{tf}, number of features to keep,
SVM regularization ($L_1$ or $L_2$ norm, strength $C$) a.o.
Such a composite \texttt{Pipeline} object
exposes all of these parameters using a special syntax;
each estimators must be given a name,
and if the SVM's name is, e.g., \texttt{linearsvm},
then its $C$ parameter is exposed as \texttt{linearsvm\_\_C}.
The pipeline's \texttt{set\_params} splits the parameter names
on double underscores, uses the first part of the result
to look up the estimator,
and passes the second part to the estimator's own \texttt{set\_params}
as a keyword argument; due to Python's dynamic parameter passing,
the result is the same as if the user had called \texttt{set\_params}
on the SVM themselves.
(The double underscore syntax is not special to pipelines;
it is also employed in ensemble estimators such as random forests
% Is the following clear? Suggestions to replace "direct attributes" with"?
It is chosen as a convention to avoid ambiguity, as direct
attributes and methods of scikit-learn objects never contain
double underscores.)

>>>>

A \texttt{FeatureUnion} object is a transformer combining multiple transformers
into a single one that joins their outputs. From an API point of view, a
\texttt{FeatureUnion} takes as input a list of transformers. Calling
\texttt{fit} on the union is the same as calling \texttt{fit} independently on
each of the transformers. For transforming data, the base transformers are
applied in parallel are their outputs are concatenated end-to-end into a larger
output.

As an example, the following snippet illustrates how to create a complex worflow
computing both PCA and Kernel PCA components on \texttt{X\_train} (through a
\texttt{FeatureUninon}), selecting the best of those features and then feeding
them to a linear model:
\begin{verbatim}
Pipeline([("pca", FeatureUnion([('linear_pca', PCA()),
                                ('kernel_pca', KernelPCA())])),
          ("feature_selection", SelectKBest()),
          ("linear_model", LinearRegression())
]).fit(X_train, y_train).predict(X_test)
\end{verbatim}

As the above snippet shows, \texttt{Pipeline} and \texttt{FeatureUninon}
can be combined to create complex objects. In particular, since both
are themselves estimators, they can be used to form nested workflows.

% A distinguishing feature of \textit{scikit-learn} estimators
% is that they can be composed into \texttt{Pipeline} objects.
% Such objects combine typical machine learning workflows
% (extracting features, centering/scaling/normalization,
% feature selection, making predictions)
% in a single object that is itself an estimator,
% and whose methods cause data to flow through the pipeline.
% More importantly, though, they can be used for
% systematic, automated model selection.
% This is best explained by example.

% By composing, say, a \texttt{CountVectorizer} object
% (which extracts term frequency features from text documents
% according to a bag-words model),
% a \textsf{tf--idf} transformer, a $\chi^2$ feature selector and a linear SVM,
% one obtains a pipeline object with various hyperparameters:
% whether to do stopword filtering,
% linear vs.\ logarithmic \textsf{tf}, number of features to keep,
% SVM regularization ($L_1$ or $L_2$ norm, strength $C$) a.o.
% Such a composite \texttt{Pipeline} object
% exposes all of these parameters using a special syntax;
% each estimators must be given a name,
% and if the SVM's name is, e.g., \texttt{linearsvm},
% then its $C$ parameter is exposed as \texttt{linearsvm\_\_C}.
% The pipeline's \texttt{set\_params} splits the parameter names
% on double underscores, uses the first part of the result
% to look up the estimator,
% and passes the second part to the estimator's own \texttt{set\_params}
% as a keyword argument; due to Python's dynamic parameter passing,
% the result is the same as if the user had called \texttt{set\_params}
% on the SVM themselves.
% (The double underscore syntax is not special to pipelines;
% it is also employed in ensemble estimators such as random forests
% % Is the following clear? Suggestions to replace "direct attributes" with"?
% It is chosen as a convention to avoid ambiguity, as direct
% attributes and methods of scikit-learn objects never contain
% double underscores.)
